---
title: "na_fix"
author: "BR"
date: "20/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(data.table)
library(zoo)
library(kableExtra)
library(qwraps2)
```

Must run entire script for raw data. rmd
```{r}
survey_final<-read.csv("data/survey_final.csv")
```

```{r}
#sapply(survey_final, function(x) sum(is.na(x)))
```


Zero NA

start	0
end	0
survey_type	0
survey_id	0
survey_version	0
country	0
community	0
sex	0
boat_status	0
boat_power	0
boat_length	0
choice	0
package_nopackage	0
fishing_organization	0
punishment_severity	0
mpa	0
age	0
years_fishing	0
education	0
digits	0

Fixed

income, enforcement, restriction, gear, fishtech, rank_one, rank_two, rank_three, rank_four




```{r}
survey<-survey_final %>%  
  mutate(sex = ifelse(survey_id == 5034, "F", "M")) %>% 
  mutate(survey_type = "data") %>%
  arrange(survey_id) %>% 
  fill(boat_status, boat_power) %>% 
  group_by(community) %>% # boat length
  mutate(boat_length = round(ifelse(is.na(boat_length), mean(boat_length, na.rm = TRUE), boat_length)), digits = 0) %>% 
  ungroup()
```


4. In the last 12 months, what fishing gear have you used? (Select all that apply)
#Refer to translation sheet https://docs.google.com/spreadsheets/d/1u1rI-I2xt75-P57bopTiFaW4rPcewF44EaAQjJcjzIc/edit#gid=0
```{r}
gear_na<-survey %>%
  select(survey_id, gear_handline:other_gear) %>%
  mutate(other_gear = as.character(other_gear)) %>% 
  mutate(gear_handline = ifelse(grepl("pancing", other_gear, ignore.case=TRUE), 1, gear_handline)) %>% 
  mutate(gear_mobilenet = ifelse(grepl("purse|payang|tarik", other_gear, ignore.case=TRUE), 1,  gear_mobilenet)) %>% 
  mutate(gear_traps = ifelse(grepl("jaring rajungan|ditebar", other_gear, ignore.case = TRUE),1, gear_traps)) %>% 
  mutate(gear_gillnet = ifelse(grepl("rampus|Jaring udang", other_gear, ignore.case = TRUE), 1 ,gear_gillnet)) %>% 
  mutate(gear_other = ifelse(grepl("angkat", other_gear, ignore.case = TRUE), 1, gear_other)) %>% 
  mutate(na_count = rowSums(is.na(.))) %>% 
  filter(na_count < 8) %>%
  mutate_all(funs(replace(., is.na(.), 0))) %>% 
  select(-na_count)
```

```{r}
fishtech_na<-survey %>%
  select(survey_id, contains('fishtech')) %>%
  mutate(other_fishtech = as.character(other_fishtech)) %>% 
  mutate(fishtech_vesseltrack = ifelse(grepl("zana", other_fishtech, ignore.case=TRUE), 1, fishtech_vesseltrack)) %>% 
  fill(starts_with('fishtech')) %>% 
  mutate(fishtech_vhf = ifelse(grepl("radio", other_fishtech, ignore.case=TRUE), 1, fishtech_vhf)) 
```

27. What regulations exist for your #1 targeted fishery? (Select all that apply)
⬜	a. Gear Restrictions
⬜	b. Size Restrictions
⬜	c. Seasonal Restrictions
⬜	d. Spatial Restrictions
⬜	e. Quotas
⬜	f. Other  _______________________
⬜	g. None

```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

restriction_na<-survey %>%
  select(survey_id, community, contains('restriction_')) %>%
  group_by(community) %>% 
  mutate(restriction_gear= na.aggregate(restriction_gear, FUN=Mode),
         restriction_size = na.aggregate(restriction_size, FUN=Mode),
         restriction_season = na.aggregate(restriction_season, FUN=Mode),
         restriction_spacial = na.aggregate(restriction_spacial, FUN=Mode),
         restriction_quota = na.aggregate(restriction_quota, FUN=Mode),
         restriction_other = na.aggregate(restriction_other, FUN=Mode),
         restriction_none = na.aggregate(restriction_none, FUN=Mode))
```

28. Who is responsible for enforcement in your community? (Select all that apply)
⬜	a. Community Members
⬜	b. Village customary leader
⬜	c. Village Government
⬜	d. Provincial Government
⬜	e. National Government
⬜	f. No Enforcement
⬜	g. Other _______________________

                          
```{r}
enforcement_na<-survey %>%
  select(survey_id, community, contains('enforcement_'), -enforcement_interval) %>%
  group_by(community) %>% 
  mutate(enforcement_community_members = na.aggregate(enforcement_community_members, FUN=Mode),
       enforcement_village_leader = na.aggregate(enforcement_village_leader, FUN=Mode),
       enforcement_village_gov = na.aggregate(enforcement_village_gov, FUN=Mode),
       enforcement_provincial_gov = na.aggregate(enforcement_provincial_gov, FUN=Mode),
       enforcement_national_gov = na.aggregate(enforcement_national_gov, FUN=Mode),
       enforcement_none = na.aggregate(enforcement_none, FUN=Mode),
       enforcement_other = na.aggregate(enforcement_other, FUN=Mode))

#df1<-enforcement_na %>%
#   select(-survey_id) %>%
#   mutate_if(is.numeric,as.factor) %>% 
#   gather(key = "enf", value = "ans", - community) %>%
#   group_by(community, enf) %>% 
#   count(ans) %>% 
#   spread(key = enf, value = n)
```
34. Please rank the following problems. 
		a. Trash polluting the ocean	
		b. Illegal Fishing	
		c. Extreme Weather	
		d. Corruption of fishing authorities
		
rank_one	5
rank_two	6
rank_three	7
rank_four	11
```{r}
rank_na<-survey %>%
  select(survey_id, community, contains('rank_')) %>%
  group_by(community) %>% 
  mutate(rank_one = na.aggregate(rank_one, FUN=Mode),
       rank_two = na.aggregate(rank_two, FUN=Mode),
       rank_three = na.aggregate(rank_three, FUN=Mode),
       rank_four = na.aggregate(rank_four, FUN=Mode))
```

35. In the last few years, the current fish catch has…		
◯	a. Declined a lot		
◯	b. Declined slightly		
◯	c. Stayed the same		
◯	d. Improved slightly		
◯	e. Improved a lot		

NA - 1
```{r}

```

42. What is your average monthly income? (INR/MEX)
income-8 missing
Converted all to USD
```{r}
#HUGE distribution of income in IND, especially in WKB (10^7 difference) min is a single digit number, which does not make sense for Indonesia (Annual income for lowest income would be $0.0043) 

#Fixing for Wkb income error & currency conversion 

#0.000071 USD / 1 Indonesian Rupiah 
#0.052 USD / 1 Medican Peso

income_na <- survey %>% 
  select(survey_id, country, community, income) %>%
  mutate(income_fix = ifelse(country == "IND" & income <= 10, income*1000000, income)) %>% 
  mutate(currency = ifelse(country=="MEX", 0.052, 0.000071)) %>% 
  mutate(income_usd = currency*income_fix) %>% 
  group_by(community) %>% 
  mutate(income_usd = na.aggregate(income_usd)) %>% 
  mutate(income_usd = round(income_usd, digits = 0)) %>% 
  select(survey_id, income_usd)

#checking to see if the numbers make sense
income_summary <-
  list("Monthly Income" =
       list("min" = ~ min(.data$income_usd),
            "max" = ~ max(.data$income_usd),
            "mean (sd)" = ~ qwraps2::mean_sd(.data$income_usd)))

#checking data before we fixed it. 
#income_na <- survey %>% 
#  select(community, income) %>% 
#  na.omit() %>% 
#  mutate(community = as.factor(community))

by_com <- summary_table(dplyr::group_by(income_na, community), income_summary)
kable(by_com)
```

```{r}
na_sum<-as.data.frame(colSums(is.na(survey)))
colnames(na_sum)<-"sum"
na_sum<-rownames_to_column(na_sum, "col")

complete <- na_sum %>% 
  filter(sum == 0) %>% 
  pull('col')

survey_comp<-survey %>% 
  select(complete) %>% 
  left_join(gear_na) %>% 
  left_join(fishtech_na) %>%
  left_join(enforcement_na) %>%
  left_join(restriction_na) %>%
  left_join(rank_na) %>%
  left_join(income_na) 


```

```{r}
#write.csv(survey_comp,"survey_comp.csv", row.names = FALSE)
```


